Binning Strategies and Related Loss for Large Data

### 2015-02-27 Paper.Rnw
changes during the meeting

\ktm{ A number of scatterplot adaptations have been introduced that avoid overplotting by manipulating point locations or location scales. \hh{These approaches do not help in the situation of ties in the data, which are very common for large data sets due to the finite resolution of data collection (e.g.\ airline data is collected at minute intervals).}  Generalized scatterplots \citep{Keim2010GenScatter} display all individual observations but use distortion of the point locations to avoid overlapping points. A\hh{n} extension of generalized scatterplots uses clustering and local principal components to allow ellipsoid oriented distortion to display local correlation structure in the data \citep{Janetzko2013Ellipse}. Variable binned scatterplots \citep{Hao2010visual} break the display into a non-uniform rectangular grid and resize the rows of cells according to density of points. This variable binning fragments the continuity of the axes into many segments on different scales. Theses approachs make fine data structure more visible and allows color to be reserved for a third variable instead of frequency; however, the distortion of the point locations or the axes wrap the visual display of the association between the two primary variables.} \hh{please check the spelling in the previous paragraph. }

>>>>

\ktm{ A number of scatterplot adaptations have been introduced that avoid overplotting by manipulating point locations or location scales. \hh{Address how ties in the data are dealt with, which are very common for large data sets due to the finite resolution of data collection (e.g.\ airline data is collected at minute intervals). jittering?}  Generalized scatterplots \citep{Keim2010GenScatter} display all individual observations but use distortion of the point locations to avoid overlapping points. A\hh{n} extension of generalized scatterplots uses clustering and local principal components to allow ellipsoid oriented distortion to display local correlation structure in the data \citep{Janetzko2013Ellipse}. Variable binned scatterplots \citep{Hao2010visual} break the display into a non-uniform rectangular grid and resize the rows of cells according to density of points. This variable binning fragments the continuity of the axes into many segments on different scales. Theses approachs make fine data structure more visible and allows color to be reserved for a third variable instead of frequency; however, the distortion of the point locations or the axes wrap the visual display of the association between the two primary variables.} \hh{please check the spelling in the previous paragraph. }
